### 2015-11-13 postdoctoral/gamma_functions.tex
got the nu result

>>>>

  \begin{theorem}
    If \(M\) is \(T_2\), then
    \(
      \varprojlim\{M,\nu,L\}
        \cong
      (\check L\times M)/\sim
    \) with the usual product topology, where \(\sim\) identifies every
    point in \(\{\emptyset\}\times M\cup\check L\times \{0\}\).
  \end{theorem}

  \begin{proof}
    We will extend \(\theta\) as defined in the previous lemma so that
    \(\theta(\vect 0)\) is sent to the points identified in
    \(\{\emptyset\}\times M\cup\check L\times \{0\}\).

    Consider the basic open neighborhood \([U,F]\) of \(\vect 0\) in
    \(\varprojlim\{M,\nu,L\}\). Let \(l_1\) be the least element of \(F\),
    and \(U'=\bigcap_{l\in F}U(l)\). Note that
    \(
      \{\emptyset\}\times M\cup\check L\times \{0\}
        \subseteq
      [\emptyset,(\leftarrow,l_1])\times M
      \cup
      \check L\times U'
    \). So let
    \(
      \vect x_{C,m}
        \in
      [\emptyset,(\leftarrow,l_1])\times M
    \),
    and note that as \(l_1\not\in C\), \(\vect x_{C,m}(l)=0\in U(l)\) for all
    \(l\in F\), and thus \(\vect x_{C,m}\in[U,F]\).
    Likewise if we let
    \(
      \vect x_{C,m}
        \subseteq
      \check L\times U'
    \),
    we have that \(x_{C,m}(l)\in U'\subseteq U(l)\) for all \(l\in L\), and
    thus \(\vect x_{C,m}\in[U,F]\).

    Now in \((\check L\times M)/\sim\)
    consider the basic open set formed by the union of
    \(V\times M\) containing \(\{\emptyset\}\times M\) and
    \(\check L\times W\) containing \(\check L\times \{0\}\).
    \(V=[\emptyset,B)\) for some nonempty leftward set \(B\),
    so choose \(l_0\in B\) and note that as
    \((\leftarrow,l_0]\subseteq B\) we have
    \([\emptyset,(\leftarrow,l_0])\subseteq[\emptyset,B)=V\).
    So let \(U(l_0)=W\) and note \(\vect 0\in[U,\{l_0\}]\). For any
    \(\vect x_{C,m}\in[U,\{l_0\}]\), we have two cases.

    If \(l_0\in C\), then \(\vect x_{C,m}(l)=m\in U(l_0)=W\) for all \(l\in C\),
    and \(\vect x_{C,m}(l)=0\in W\) otherwise. Thus
    \(\<C,m\>\in\check L\times W\).

    Otherwise \(l_0\not\in C\), and thus \(C\subsetneq(\leftarrow,l_0]\).
    Then as \(C\in [\emptyset,(\leftarrow,l_0])\subseteq V\),
    we have \(\<C,m\>\in V\times M\).
    \end{proof}
